Extracting data for time slice analyses

### 2017-11-29 analyses/01-extract-data-for-analyses.Rmd
Fix issues with non overlapping taxa and tree mismatch

@@

@@

@@

>>>>

One final issue is that to compute Gower distances we need all taxa to have some overlapping data. If not, Gower distances will be NA (Gower distance does not impute missing data like some other methods) and we can't estimate disparity. To avoid this problem we can remove the taxa with no overlaps using `TrimMorphDistMatrix` from `Claddis` on our distance matrix. Of course this then means we need to remove these from the tree as well. This then changes the node numbers which means we need to recalculate ancestral states. Because nothing is ever easy! Rather than going round in circles with this code, we just remove the species where this is a problem when we read in the trees (only an issue below for the Bapst and Brusatte datasets). Yes there's a more elegant way to do this, but time is tight and I'm pretty sure this project is trying to break us...

If you needed to do this for your own data, this is how you can quickly work out which taxa to remove.

```{r}
## Trimming the distance matrix
## trim <- TrimMorphDistMatrix(matrix_dist)
## matrix_dist <- trim$dist.matrix

## Which taxa were removed?
## (remove_taxa <- as.vector(trim$removed.taxa))
```

@@

## Replace zero branches with minimum branch length
tree$edge.length[which(tree$edge.length == 0)] <- 
  min(tree$edge.length[-which(tree$edge.length == 0)])

## Remove taxa with non overlapping data (see note about Gower distances above)
remove_Bapst <- c("Hagryphus_giganteus", "Atrociraptor_marshalli", "IGM100_1015_UndesDromaeosaurid", "Dromaeosaurus_albertensis", "Incisivosaurus_gauthieri", "Deinocheirus_mirificus", "Therizinosaurus_cheloniformis", "Anserimimus_planinychus", "Elmisaurus_rarus")

tree <- drop.tip(tree, remove_Bapst)

@@

## Remove taxa with non overlapping data (see note about Gower distances above)
remove_Brusatte <- c("Shanag_ashile", "Atrociraptor_marshalli", "Proceratosaurus_bradleyi",     "Incisivosaurus_gauthieri", "Enigmosaurus", "Nanshiungosaurus_brevispinus", "Xixiasaurus", "Tsaagan_mangas", "Mirischia", "Pedopenna", "Suzhousaurus", "Juratyrant", "Vorona", "Bonapartenykus", "Teratophoneus", "Gobipteryx", "Songlingornis", "Liaoningornis_longidigitu", "Achillesaurus")

tree <- drop.tip(tree, remove_Brusatte)

@@

## Remove
